Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2017-03-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
cut excess figures moved to CH 8 extra

\begin{figure}[p]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=05_0601T}\\
	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=10_601T}\\
	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=20_0600T}\\
	\caption[FDS Smokeview plume temperatures with the burner 0.61~m from the wall at approximately 180 s for the 80~mm, 40~mm, and 20~mm mesh resolution cases]{FDS Smokeview plume temperatures with the burner 0.61~m from the wall at approximately 180 s of the steady state simulation.  Beginning with the top graphic and moving down, the 80~mm, 40~mm, and 20~mm mesh resolution cases are presented.}
	\label{FDS_Plume_Temp_IWGB_Comp_}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=05_0300WT}\\
	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=10_0300WT}\\
	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=20_0300WT}\\
	\caption[FDS Smokeview wall temperatures with the burner 0.61~m from the wall at approximately 180 s for the 80~mm, 40~mm, and 20~mm mesh resolution cases]{FDS Smokeview wall temperatures with the burner 0.61~m from the wall at approximately 180 s of the steady state simulation.  Beginning with the top graphic and moving down, the 80~mm, 40~mm, and 20~mm mesh resolution cases are presented.}
	\label{FDS_Wall_Temp_IWGB_Comp_}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_2D_RI=10_0300WT}
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_1D_RI=10_0300WT}\\
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_p5D_RI=10_0300WT}
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_0D_RI=10_0300WT}\\
  \caption[FDS wall temperatures based on 40~mm grid compared with natural gas burner different distances from the wall]{FDS wall temperatures based on 40~mm grid compared with natural gas burner different distances from the wall. Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_TCWall_IWGB_comp}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_2D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_1D}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0p5D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D}\\
  \caption[FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.]{FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner. The heat fluxes are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_HFCL_IWNG_comp}
\end{figure}{}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_2D_RI=10_0300HF}
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_1D_RI=10_0300HF}\\
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_p5D_RI=10_0300HF}
  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_0D_RI=10_0300HF}\\
  \caption[FDS gauge heat flux values based on 40~mm grid with natural gas burner positioned different distances from the wall]{FDS gauge heat flux values based on 40~mm grid with natural gas burner positioned different distances from the wall. Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_WallHF_IWGB_comp}
\end{figure}

>>>>

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_2D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_1D}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0p5D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D}\\
  \caption[FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.]{FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner. The heat fluxes are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_HFCL_IWNG_comp}
\end{figure}

@@
